Renaming The Amplicons and Tidying up the Amplicon Information Table

### 2024-07-02 extras/Renaming-amplicons/Amplicon-renaming.Rmd
Revamped Amplicon Info to have SNP positions...
...relative to the actual amplicon that maps, so that we can calculate the Otsh_v2.0 position easily.

@@

```{r}
write_csv(final, "../../inputs/Calif-Chinook-Amplicon-Panel-Information.csv", na = "")
```

>>>>

## Deal with the different between ReferenceSequence and TrimmedAmpliconSequence

So, the `RefereneSequence` is sometimes the same as the TrimmedAmpliconSequence, and
sometimes it is not. Mostly it is not the same for the WRAP and LFAR and RoSA, etc.
So, this is not a huge problem.  In cases where things are not the same, the ReferenceSequence
was the sequence I sent to Anthony to design the primers, while the TrimmedAmpliconSequence
is what is actually amplified and what actually gets mapped to the Otsh_V1.0 genome.
So, when we want to figure out the actual position in the genome of particular variants,
we need to know their position in the TrimmedAmpliconSequence, but we actually
only have it in the ReferenceSequence.

So, we have to do some modifications here to make sure we have the position
in the variants in the actualy amplicon sequence.  We can do that pretty
easily.

I am going to rename things a little bit so ReferenceSequence becomes DesignSequence, and
TrimmedAmpliconSequence becomes "AmpliconSequence".

```{r}
# we first need a function to modify the snp locations
# pos is the current list column of positions
# as is the amplicon start position in the reference sequence
new_locations <- function(pos, as, ae) {
  amp_length = ae - as
  pvec <- lapply(str_split(pos, ", *"), as.integer)
  altered_pvec <- map2(.x = pvec, .y = as, .f = function(x, y) x - y + 1)
  thinned_pvec <- map2(.x = altered_pvec, .y = amp_length, .f = function(x, y) x[x > 0 & x <= y])
  ret <- map_chr(.x = thinned_pvec, .f = function(x) paste(x, collapse = ", "))
  unlist(ret)
}

tmp <- final %>%
  mutate(
    ampli_start = str_locate(ReferenceSequence, TrimmedAmpliconSequence)[,1],
    ampli_end = str_locate(ReferenceSequence, TrimmedAmpliconSequence)[,2],
    .before = AmpliconName
  ) %>%
  mutate(
    SNPLocationsInAmpliconSequence = pmap_chr(
      .l = list(pos = SNPLocationsInReferenceSequence, as = ampli_start, ae = ampli_end),
      .f = new_locations
    ),
    .after = SNPLocationsInReferenceSequence
  )

# then, pick out columns in the right order
real_final <- tmp %>% 
  select(
    AmpliconName, 
    Otsh_v2.0_chromosome, 
    AmpliconStartPos, 
    LocusOrigin, 
    OriginalReference, 
    OtherName, 
    ForwardPrimerSequence, 
    ReversePrimerSequence, 
    TrimmedAmpliconSequence,
    SNPLocationsInAmpliconSequence, 
    Otsh_v2.0_coordinates, 
    Alternate_Otsh_v2.0_coordinates, 
    Otsh_v1.0_coordinates, 
    Alternate_Otsh_v1.0_coordinates, 
    MappingNotes,
    ReferenceSequence, 
    SNPLocationsInReferenceSequence, 
  ) %>%
  rename(
    AmpliconSequence = TrimmedAmpliconSequence,
    DesignSequence = ReferenceSequence,
    SNPLocationsInDesignSequence = SNPLocationsInReferenceSequence
  ) %>%
  mutate(
    SNPLocationsInAmpliconSequence = ifelse(SNPLocationsInAmpliconSequence == "NA", NA, SNPLocationsInAmpliconSequence)
  )
```

## Print that dude out

@@

```{r}
write_csv(real_final, "../../inputs/Calif-Chinook-Amplicon-Panel-Information.csv", na = "")
write_csv(real_final, "../../tex/supp_data/Supp-Data-1-Amplicon-info.csv", na = "")
```
